Supplementary material: The increasing cost of happiness

### 2021-05-27 src/draft-html0.Rmd
SSM0 Population Health submission

---
title: "The increasing cost of happiness"
author: "R.W. Morris^1,2^, N. Kettlewell^2,3,4^  & N.Glozier^1,2^"
bibliography: ../src/references.bib
csl: ../src/elsevier-harvard.csl
output:  
  word_document:
    reference_docx: ../src/Rmarkdown-for-Word-styles.docx
always_allow_html: yes
editor_options: 
  chunk_output_type: console
---

@@

## Significance Statement
Income has decreasing returns on happiness, across countries, cultures and ethnicities, with an inflection or change point near USD75,000. Below this point, happiness is relatively dependent on income levels; revealing an inequity in the distribution of happiness between rich and poor. We do not know whether or how this point changes over time. Has it decreased and reduced inequity, or increased the difference between the rich and poor? We examine 19 years of data from Australia and determine that the income level at which happiness becomes less influenced by income has increased, relative to the cost of living. The happiness of an increasing proportion of the population is more dependent on their financial security than ever this millennium. (120 max)

@@

Supplementary information is available [online](https://datarichard.github.io/The-increasing-cost-of-happiness/supplementary.html.

>>>>

---
title: "The increasing cost of happiness"
author: "R.W. Morris^1,2^, N. Kettlewell^2,3,4^  & N.Glozier^1,2^"
bibliography: ../src/references.bib
csl: ../src/elsevier-harvard.csl
output:  
  html_document:
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: false
always_allow_html: yes
editor_options: 
  chunk_output_type: console
---

@@

## Significance Statement

Income has decreasing returns on happiness, across countries, cultures and ethnicities, with an inflection or change point near USD75,000. Below this point, happiness is relatively dependent on income levels; revealing an inequity in the distribution of happiness between rich and poor. We do not know whether or how this point changes over time. Has it decreased and reduced inequity, or increased the difference between the rich and poor? We examine 19 years of data from Australia and determine that the income level at which happiness becomes less influenced by income has increased, relative to the cost of living. The happiness of an increasing proportion of the population is more dependent on their financial security than ever this millennium. (120 max)

@@

Supplementary information is available [online](https://datarichard.github.io/The-increasing-cost-of-happiness/supplementary.html){target="_blank"}.

### 2021-05-27 src/supplementary-SSM0.Rmd
SSM0 Population Health submission

---
title: "Supplementary material: The increasing cost of happiness"
author: "R.W. Morris^1,2^, N. Kettlewell^2,3,4^  & N.Glozier^1,2^"
bibliography: ../src/references.bib
csl: ../src/elsevier-harvard.csl
output:  
  word_document:
    reference_docx: ../src/Rmarkdown-for-Word-styles.docx
always_allow_html: yes
editor_options: 
  chunk_output_type: console
---

@@

1. Central Clinical School, Faculty of Medicine and Health, University of Sydney, NSW, Australia
2. ARC Centre of Excellence for Children and Families over the Life Course
3. School of Economics, University of Technology, NSW, Australia
4. Institute of Labor Economics (IZA), Bonn, Germany

**Corresponding author:**  
Professor Nick Glozier  
Faculty of Medicine and Health,   
University of Sydney,  
NSW 2050,  
Australia  
email: nick.glozier@sydney.edu.au

@@

There were _N_ = 59,876 total observations. 4000 samples (post-warmup) were drawn using sampling(NUTS). For each parameter, Bulk_ESS and Tail_ESS are effective sample size (ESS) measures, and Rhat is the potential scale reduction factor on split chains. In each case the Rhat approached 1, indicating convergance. Each ESS _n_ > 300, which is a conservative threshold for estimation.

>>>>

---
title: "Supplementary material: The increasing cost of happiness"
bibliography: ../src/references.bib
csl: ../src/elsevier-harvard.csl
output:  
  html_document:
    reference_docx: ../src/academic_style.docx
always_allow_html: yes
editor_options: 
  chunk_output_type: console
---

@@

@@

Model fitting was performed in RStan (v2.21.2) using the brms (v2.14.4) package [@burkner2017; @rstan2019]. There were _N_ = 59,876 total observations. 4000 samples (post-warmup) were drawn using sampling(NUTS). For each parameter, Bulk_ESS and Tail_ESS are effective sample size (ESS) measures, and Rhat is the potential scale reduction factor on split chains. In each case the Rhat approached 1, indicating convergance. Each ESS _n_ > 300, which is a conservative threshold for estimation.
